Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks

### 2023-05-11 paper.tex
minor

 the goal of a \ac{GNN} is to learn the node embedding $h_v$ for each node $v \in V$. The node embedding $h_v$ describes the node in the network and summarise the geometric properties of the graph in this location, allowing for comparison of various nodes in the graph.

>>>>

 the goal of a \ac{GNN} is to learn the node embedding $h_v$ for each node $v \in V$. The node embedding $h_v$ describes the node in the network and summarises the geometric properties of the graph in this location, allowing for comparison of various nodes in the graph.
